Efficient Thresholded Correlation using Truncated Singular Value Decomposition

### 2017-08-10 threshold/draft.Rnw
General Matrices is now it's own section.

\subsection{Thresholded correlation of columns between two different matrices}

WRITE ME

\subsection{Alternative metrics}

The idea of evaluating threshold conditions by projection into low dimensional
subspaces applies to distance metrics similarly to correlation, see
\cite{svd-similarity} for a related approach. Lemma \ref{sumlemma} decomposes
Euclidean distance between two vectors in terms of singular basis vectors and
Algorithm \ref{prune} can be applied directly to the problem of finding all
pairs of vectors that meet a thresholded Euclidean distance with small changes
in steps 3, 4, and 7.  By equivalence of norms, thresholded Euclidean distance
can be extended to other distance metrics. The reference \proglang{R}
implementation \cite{sup} includes functions for thresholded distance and
correlation.

>>>>

\subsection{Spearman correlation}

TODO: WRITE THIS
The idea of evaluating threshold conditions by projection into low dimensional
subspaces applies to distance metrics similarly to correlation, see
\cite{svd-similarity} for a related approach. Lemma \ref{sumlemma} decomposes
Euclidean distance between two vectors in terms of singular basis vectors and
Algorithm \ref{prune} can be applied directly to the problem of finding all
pairs of vectors that meet a thresholded Euclidean distance with small changes
in steps 3, 4, and 7.  By equivalence of norms, thresholded Euclidean distance
can be extended to other distance metrics. The reference \proglang{R}
implementation \cite{sup} includes functions for thresholded distance and
correlation.

\subsection{Most correlated pairs}

TODO: WRITE THIS
